---
title: "Project of Foundations of Probability and Statistics"
author: "Paola Cavana, Julia Tsymbal"
date: "2022-2023"
output:
  html_document:
    toc: yes
    number_sections: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Main goal of this analysis is to predict insurance costs for customers.

[Link al dataset](https://www.kaggle.com/datasets/mirichoi0218/insurance?resource=download)

Columns:

- age: age of primary beneficiary

- sex: insurance contractor gender, female, male

- bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height,
objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

- children: Number of children covered by health insurance / Number of dependents

- smoker: Smoking

- region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

- charges: Individual medical costs billed by health insurance

The formula of the BMI consists in the division of the weight of an adult subject, expressed in kilograms (kg), by the square of its height expressed in meters (m).
 
Category: 

BMI range (kg/m2). 

- Obesity class III (very serious): > 40,00. 

- Obesity class II (severe): 35,01 to 40,00. 

- Obesity class I (moderate): 30,01 to 35,00.

- Overweight: 25,01 to 30,00. 

- Regular: 18,51 to 25,00. 

- Slightly underweight: 17,51 to 18,50. 

- Underweight: 16,01 to 17,50. 

- Severe leanness (starvation): <16,01 



## Requirements

- install.packages("ggplot2")
- install.packages("ggpubr")
- install.packages("GGally")
- install.packages("ggpairs")
- install.packages("wesanderson")
- install.packages("modest")
- install.packages("MASS")
- install.packages("dplyr")
- install.packages("caret")
- install.packages("tidyverse")
- install.packages("patchwork")
- install.packages("ggforce")

```{r}
library(ggplot2) 
library(ggpubr)
library(ggcorrplot) 
library(RColorBrewer)
library(wesanderson) 
library(modest)
library(MASS)
library(dplyr)
library(caret)
library(tidyverse)
library(patchwork)
library(ggforce)
```


# Data Exploration

we load the dataset:

```{r}
insurance <- read.table("insurance.csv", header = TRUE, sep = ",")
```

Once the file is loaded, it is useful to carry out an exploratory analysis to observe its contents and features.

```{r}
dim(insurance)
```

As we can see from the output, the dataset consists of 1338 rows and 7 columns.

```{r}
colnames(insurance)
```

Look at the head and tail of the datasets:

```{r}
head(insurance)
```

```{r}
tail(insurance)
```

With the following code we verify the data type of the variables.

```{r}
str(insurance)
```

We can observe that 2 variables are of type 'numeric', 3 variables are of type 'char' and 2 variables are of type 'integer'. 

We know that the typology 'integer' constitutes a subclass of the typology 'numeric', and has the characteristic to occupy less space in memory.



At this point we verify the presence of null or missing values.

```{r}
insurance[rowSums(is.na(insurance)) > 0, ]
```

The result of this function does not return lines, therefore inside the dataset there are no null or missing values.


# Descriptive Statistics

Let’s proceed with the descriptive analysis of the dataset. 

```{r} 
summary(insurance) 
```

From the summary we can see some interesting features and pay attention to:

- The age of individuals varies from 18 to 64 years.

- The mean of bmi is 30.66 so we can say that the average individuals are in "Obesity class I (moderate)" class.

- Datasets individuals have an average child.

- From the charges summary we can notice that there is a big difference between min and max.


## Variables

### Charges

```{r}
brx_Charges <- pretty(range(insurance$charges),
              n = nclass.Sturges(insurance$charges), min.n = 1)

Charges1 <- ggplot(insurance) +
  geom_histogram(aes(x=charges), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_Charges) +
  geom_vline(aes(xintercept=mean(charges)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Charges", y="Count") +
  theme_classic()

Charges2 <- ggplot(insurance, aes(x = "", y=charges)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "charges") +
  theme_minimal()

ggarrange(Charges1, Charges2,
          ncol = 2,
          nrow = 1)
```

```{r}
p2<-ggplot(insurance, aes(x=sex, y=charges)) +
geom_boxplot(fill=c('hotpink', "royalblue"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

p3<-ggplot(insurance, aes(x=smoker, y=charges)) +
geom_boxplot(fill=c('grey', "gold"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

p4<-ggplot(insurance, aes(x=region, y=charges)) +
geom_boxplot(fill=c('tan1', "tan2", 'tan3', "tan4"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

ggarrange(p2, p3, p4,
          ncol = 1,
          nrow = 1)
```


```{r}
ordered_Charges <- insurance[order(-insurance$charges), ]

head(ordered_Charges)

tail(ordered_Charges)
```

```{r}
boxplot.stats(insurance$charges)
```

### Age

```{r}
brx_age <- pretty(range(insurance$age),
              n = nclass.Sturges(insurance$age), min.n = 1)

Age1 <- ggplot(insurance) +
  geom_histogram(aes(x=age), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_age) +
  geom_vline(aes(xintercept=mean(age)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Age", y="Count") +
  theme_classic()

Age2 <- ggplot(insurance, aes(x = "", y=age)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Age") +
  theme_minimal()

Age3 <- ggplot(insurance, aes(age)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Age") +
  theme_classic()

Age4 <- ggplot(insurance) +
  geom_point(aes(x=age, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Age")

ggarrange(Age1, Age2, Age3, Age4,
          ncol = 2,
          nrow = 2)
```

#### age & sex, charges
```{r}
as1<-ggplot(insurance, aes(x=sex, y=age, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="Age Distribution by sex")+
theme(plot.title = element_text(size=14))

as2<-ggplot(insurance, aes(x=age, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(as1, as2,
          ncol = 2,
          nrow = 1)
```

#### age & smoker, charges
```{r}
ass1<-ggplot(insurance, aes(x=smoker, y=age, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title="Age Distribution by smoker")+
theme(plot.title = element_text(size=14))

ass2<-ggplot(insurance, aes(x=age, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(ass1, ass2,
          ncol = 2,
          nrow = 1)
```

#### age & region, charges
```{r}
ar1<-ggplot(insurance, aes(x=region, y=age, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="Age Distribution by region")+
theme(plot.title = element_text(size=14))

ar2<-ggplot(insurance, aes(x=age, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(ar1, ar2,
          ncol = 2,
          nrow = 1)
```

#### Conclusion age

```{r}
ordered_Age <- insurance[order(-insurance$age), ]

head(ordered_Age)

tail(ordered_Age)
```

```{r}
boxplot.stats(insurance$age)
```

### Sex

```{r}
mode = function(){
    return(sort(-table(insurance$sex))[1])
}
 
mode()

sex = insurance$sex

sex.freq = table(sex)

pie(sex.freq, col=c('hotpink', "royalblue"))

SexBar <- ggplot(insurance) +
  geom_bar(aes(x=sex), width = 0.5, fill=c('hotpink', "royalblue"), color="black") +
  labs(title="",x="Sex", y="Count") +
  theme_classic()

ggarrange(SexBar)

```

```{r} 
table(insurance$sex) 
```
- There are 662 females and 676 males.

### Bmi

```{r}
brx_bmi <- pretty(range(insurance$bmi),
              n = nclass.Sturges(insurance$bmi), min.n = 1)

Bmi1 <- ggplot(insurance) +
  geom_histogram(aes(x=bmi), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_bmi) +
  geom_vline(aes(xintercept=mean(age)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Bmi", y="Count") +
  theme_classic()

Bmi2 <- ggplot(insurance, aes(x = "", y=bmi)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Bmi") +
  theme_minimal()

Bmi3 <- ggplot(insurance, aes(bmi)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Bmi") +
  theme_classic()

Bmi4 <- ggplot(insurance) +
  geom_point(aes(x=bmi, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Bmi")

ggarrange(Bmi1, Bmi2, Bmi3, Bmi4,
          ncol = 2,
          nrow = 2)
```

#### bmi & sex, charges
```{r}
bs1<-ggplot(insurance, aes(x=sex, y=bmi, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="BMI Distribution by sex")+
theme(plot.title = element_text(size=14))

bs2<-ggplot(insurance, aes(x=bmi, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(bs1, bs2,
          ncol = 2,
          nrow = 1)
```

#### bmi & smoker, charges
```{r}
bss1<-ggplot(insurance, aes(x=smoker, y=bmi, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title="BMI Distribution by smoker")+
theme(plot.title = element_text(size=14))

bss2<-ggplot(insurance, aes(x=bmi, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(bss1, bss2,
          ncol = 2,
          nrow = 1)
```

#### bmi & region, charges
```{r}
br1<-ggplot(insurance, aes(x=region, y=bmi, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="BMI Distribution by region")+
theme(plot.title = element_text(size=14))

br2<-ggplot(insurance, aes(x=bmi, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(br1, br2,
          ncol = 2,
          nrow = 1)
```

#### Conclusion bmi

```{r}
ordered_Bmi <- insurance[order(-insurance$bmi), ]

head(ordered_Bmi)

tail(ordered_Bmi)
```

```{r}
boxplot.stats(insurance$bmi)
```

### Children 

```{r}
Child1 <- ggplot(insurance) +
  geom_bar(aes(x=children), fill = wes_palette("Zissou1")[1], color="black") +
  geom_vline(aes(xintercept=mean(children)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Children", y="Count") +
  theme_classic()

Child2 <- ggplot(insurance, aes(x = "", y=children)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Children") +
  theme_minimal()

Child3 <- ggplot(insurance, aes(children)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Children") +
  theme_classic()

Child4 <- ggplot(insurance) +
  geom_point(aes(x=children, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Children")

ggarrange(Child1, Child2, Child3, Child4,
          ncol = 2,
          nrow = 2)
```

#### children & sex, charges
```{r}
cs1<-ggplot(insurance, aes(x=sex, y=children, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="Children Distribution by sex")+
theme(plot.title = element_text(size=14))

cs2<-ggplot(insurance, aes(x=children, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(cs1, cs2,
          ncol = 2,
          nrow = 1)
```

#### children & smoker, charges
```{r}
css1<-ggplot(insurance, aes(x=smoker, y=children, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title=" Children Distribution by smoker")+
theme(plot.title = element_text(size=14))

css2<-ggplot(insurance, aes(x=children, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(css1, css2,
          ncol = 2,
          nrow = 1)
```

#### children & region, charges
```{r}
cr1<-ggplot(insurance, aes(x=region, y=children, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="Children Distribution by region")+
theme(plot.title = element_text(size=14))

cr2<-ggplot(insurance, aes(x=children, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(cr1, cr2,
          ncol = 2,
          nrow = 1)
```

### Smoker
```{r}
mode = function(){
    return(sort(-table(insurance$smoker))[1])
}
 
mode()

smoker = insurance$smoker

smoker.freq = table(smoker)

pie(smoker.freq, col=c('grey', "gold"))

SmokerBar <- ggplot(insurance) +
  geom_bar(aes(x=smoker), width = 0.5, fill = c('grey', "gold"), color="black") +
  labs(title="",x="Smoker", y="Count") +
  theme_classic()

ggarrange(SmokerBar)
```

```{r} 
table(insurance$smoker) 
```
- 274 individals smoke and 1064 individuals doesn't smoke.

### Region
```{r}
mode = function(){
    return(sort(-table(insurance$region))[1])
}
 
mode()

region = insurance$region

region.freq = table(region)

pie(region.freq, col = c('tan1', "tan2", 'tan3', "tan4"))

RegionBar <- ggplot(insurance) +
  geom_bar(aes(x=region), width = 0.5, fill=c('tan1', "tan2", 'tan3', "tan4"), color="black") +
  labs(title="",x="Region", y="Count") +
  theme_classic()

ggarrange(RegionBar)
```


# Correlation

Correlation is a statistical measure that expresses the extent to which two variables are linearly related.

```{r}
cor(insurance$charges, insurance$bmi)
```

There is no relationship between bmi and charges


```{r}
cor(insurance$charges, insurance$age)
```

There is no relationship between age and charges

```{r}
cor(insurance$charges, insurance$children)
```

There is no relationship between children and charges

```{r}
aggregate(cbind(age, bmi, charges) ~ region + smoker,
  data = insurance,
  mean
)
```

```{r}
shapiro.test(insurance$charges)

shapiro.test(insurance$age)
```

Low p-values so we reject the null hypothesis of normality.

```{r}
cor.test(insurance$charges, insurance$age, method="kendall")
```

Significant correlation. 0.47


# Tests

```{r}
t.test(insurance$bmi, mu = 30, 
       alternative="two.sided") # (one-tailed test)
```

The null hypothesis is mean = 30. 
The p-value is less than a significance level of 5%.
So we can reject the null hipothesis of mean = 30, and this means that the mean bmi is significantly different from 30.

Shapiro test to see if it's normally distributed.
```{r}
shapiro.test(insurance$bmi)
```

It is not normally distributed, so we use Wilcoxon test

```{r}
wilcox.test(insurance$bmi, mu = 30,  
            alternative="two.sided") # assuming the distribution is simetricaly aroud median
```

With p-value is less then 5%, I can reject the null hypothesis of mean = 30. 
The mean is statisticaly different from 30.

Is the male bmi mean equal to the female bmi mean?
```{r}
var.test(insurance[which(insurance$sex=="male"), "bmi"], 
         insurance[which(insurance$sex=="female"), "bmi"])
```

The null hypothesis is same variance. 
The p-values greater then the significance level of 0.05 allows us to accept the null hipothesis of two normal samples with same variance. 

t-test 
```{r}
t.test(insurance[which(insurance$sex=="male"), "bmi"],
       insurance[which(insurance$sex=="female"), "bmi"], 
       alternative="two.sided", 
       var.equal= TRUE)
```

p-value greater than 0.05 so we can accept the null hypothesis of equal average bmi (not significantly different) between men and women.

Shapiro Test for variable male
```{r}
shapiro.test(insurance[which(insurance$sex=="male"), "bmi"])
```

Shapiro Test for variable male
```{r}
shapiro.test(insurance[which(insurance$sex=="female"), "bmi"])
```

The p-value smaller then 0.05 for both cases so we reject the null hipothesis of normally distribution.

Wilcoxon test
```{r}
wilcox.test(insurance[which(insurance$sex=="male"), "bmi"], 
            insurance[which(insurance$sex=="female"), "bmi"])
```

p-value greater then 5 % allow us to accept the null hipothesis of median bmi equal (not significantly diferent) for man and women.

## Anova Test
Test of the hypothesis used to determine whether there is a significant statistical difference between the averages of three or more groups of continuous data with respect to a category that differentiates them.

```{r}
anova<-aov(bmi ~ smoker,  data=insurance)
summary(anova)
```

The p-value is 0.891, so we can't reject the null hypothesis of equal means.

```{r}
shapiro.test(x=residuals(object = anova))
```

```{r}
kruskal.test(bmi ~ smoker,  data=insurance)
```


```{r}
anova2<-aov(bmi ~ region,  data=insurance)
summary(anova2)
```

Low p-value, so we can reject the null hypothesis of equal means.

```{r}
shapiro.test(x=residuals(object = anova2))
```

```{r}
kruskal.test(bmi ~ region,  data=insurance)
```

# Regression







