---
title: "ProjectR"
author: "Paola Cavana, Julia Tsymbal"
output: html_document
date: "2022-2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Main goal of this analysis is to predict insurance costs for customers.

[Link al dataset](https://www.kaggle.com/datasets/mirichoi0218/insurance?resource=download)

Columns:

- age: age of primary beneficiary

- sex: insurance contractor gender, female, male

- bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height,
objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

- children: Number of children covered by health insurance / Number of dependents

- smoker: Smoking

- region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

- charges: Individual medical costs billed by health insurance

The formula of the BMI consists in the division of the weight of an adult subject, expressed in kilograms (kg), by the square of its height expressed in meters (m).
 
Category: 

BMI range (kg/m2). 

- Obesity class III (very serious): > 40,00. 

- Obesity class II (severe): 35,01 to 40,00. 

- Obesity class I (moderate): 30,01 to 35,00.

- Overweight: 25,01 to 30,00. 

- Regular: 18,51 to 25,00. 

- Slightly underweight: 17,51 to 18,50. 

- Underweight: 16,01 to 17,50. 

- Severe leanness (starvation): <16,01 



## Requirements

- install.packages("ggplot2")
- install.packages("ggpubr")
- install.packages("GGally")
- install.packages("ggpairs")
- install.packages("wesanderson")

```{r}
library(ggplot2) 
library(ggpubr)
library(ggcorrplot) 
library(RColorBrewer)
library(wesanderson) 
```

## Data Exploration

we load the dataset:

```{r}
insurance <- read.table("insurance.csv", header = TRUE, sep = ",")
```

Once the file is loaded, it is useful to carry out an exploratory analysis to observe its contents and features.

```{r}
dim(insurance)
```

As we can see from the output, the dataset consists of 1338 rows and 7 columns.

```{r}
colnames(insurance)
```

Look at the head and tail of the datasets:

```{r}
head(insurance)
```

```{r}
tail(insurance)
```

With the following code we verify the data type of the variables.

```{r}
str(insurance)
```

We can observe that 2 variables are of type 'numeric', 3 variables are of type 'char' and 2 variables are of type 'integer'. 

We know that the typology 'integer' constitutes a subclass of the typology 'numeric', and has the characteristic to occupy less space in memory.

At this point we verify the presence of null or missing values.

```{r}
insurance[rowSums(is.na(insurance)) > 0, ]
```

The result of this function does not return lines, therefore inside the dataset there are no null or missing values.

## Descriptive Statistics

Let’s proceed with the descriptive analysis of the dataset. 

```{r} 
summary(insurance) 
````

From the summary we can see some interesting features and pay attention to:

- The age of individuals varies from 18 to 64 years.

- The mean of bmi is 30.66 so we can say that the average individuals are in "Obesity class I (moderate)" class.

- Datasets individuals have an average child.

- From the charges summary we can notice that there is a big difference between min and max.

```{r} 
sum(insurance$sex=='female') 
````
```{r} 
sum(insurance$sex=='male') 
````

- There are 662 females and 676 males.

```{r} 
sum(insurance$smoker=='yes') 
````
```{r} 
sum(insurance$smoker=='no') 
````

- 274 individals smoke and 1064 individuals doesn't smoke.

## Variables
