---
title: "Project of Foundations of Probability and Statistics"
author: "Paola Cavana, Julia Tsymbal"
date: "2022-2023"
output:
  html_document:
    toc: yes
    number_sections: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Main goal of this analysis is to predict insurance costs for customers.

[Link al dataset](https://www.kaggle.com/datasets/mirichoi0218/insurance?resource=download)

Columns:

- age: age of primary beneficiary

- sex: insurance contractor gender, female, male

- bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height,
objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

- children: Number of children covered by health insurance / Number of dependents

- smoker: Smoking

- region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

- charges: Individual medical costs billed by health insurance

The formula of the BMI consists in the division of the weight of an adult subject, expressed in kilograms (kg), by the square of its height expressed in meters (m).
 
Category: 

BMI range (kg/m2). 

- Obesity class III (very serious): > 40,00. 

- Obesity class II (severe): 35,01 to 40,00. 

- Obesity class I (moderate): 30,01 to 35,00.

- Overweight: 25,01 to 30,00. 

- Regular: 18,51 to 25,00. 

- Slightly underweight: 17,51 to 18,50. 

- Underweight: 16,01 to 17,50. 

- Severe leanness (starvation): <16,01 



## Requirements

- install.packages("ggplot2")
- install.packages("ggpubr")
- install.packages("GGally")
- install.packages("ggpairs")
- install.packages("wesanderson")
- install.packages("modest")
- install.packages("MASS")
- install.packages("dplyr")
- install.packages("caret")
- install.packages("tidyverse")
- install.packages("patchwork")
- install.packages("ggforce")
- install.packages("car")

```{r}
library(ggplot2) 
library(ggpubr)
library(ggcorrplot) 
library(RColorBrewer)
library(wesanderson) 
library(modest)
library(MASS)
library(dplyr)
library(caret)
library(tidyverse)
library(patchwork)
library(ggforce)
library(car)
```


# Data Exploration

we load the dataset:

```{r}
insurance <- read.table("insurance.csv", header = TRUE, sep = ",")
```

Once the file is loaded, it is useful to carry out an exploratory analysis to observe its contents and features.

```{r}
dim(insurance)
```

As we can see from the output, the dataset consists of 1338 rows and 7 columns.

```{r}
colnames(insurance)
```

Look at the head and tail of the datasets:

```{r}
head(insurance)
```

```{r}
tail(insurance)
```

With the following code we verify the data type of the variables.

```{r}
str(insurance)
```

We can observe that 2 variables are of type 'numeric', 3 variables are of type 'char' and 2 variables are of type 'integer'. 

We know that the typology 'integer' constitutes a subclass of the typology 'numeric', and has the characteristic to occupy less space in memory.



At this point we verify the presence of null or missing values.

```{r}
insurance[rowSums(is.na(insurance)) > 0, ]
```

The result of this function does not return lines, therefore inside the dataset there are no null or missing values.


# Descriptive Statistics

Let’s proceed with the descriptive analysis of the dataset. 

```{r} 
summary(insurance) 
```

From the summary we can see some interesting features and pay attention to:

- The age of individuals varies from 18 to 64 years.

- The mean of bmi is 30.66 so we can say that the average individuals are in "Obesity class I (moderate)" class.

- Datasets individuals have an average child.

- From the charges summary we can notice that there is a big difference between min and max.


## Variables

### Charges

```{r}
brx_Charges <- pretty(range(insurance$charges),
              n = nclass.Sturges(insurance$charges), min.n = 1)

Charges1 <- ggplot(insurance) +
  geom_histogram(aes(x=charges), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_Charges) +
  geom_vline(aes(xintercept=mean(charges)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Charges", y="Count") +
  theme_classic()

Charges2 <- ggplot(insurance, aes(x = "", y=charges)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "charges") +
  theme_minimal()

ggarrange(Charges1, Charges2,
          ncol = 2,
          nrow = 1)
```

```{r}
p2<-ggplot(insurance, aes(x=sex, y=charges)) +
geom_boxplot(fill=c('hotpink', "royalblue"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

p3<-ggplot(insurance, aes(x=smoker, y=charges)) +
geom_boxplot(fill=c('grey', "gold"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

p4<-ggplot(insurance, aes(x=region, y=charges)) +
geom_boxplot(fill=c('tan1', "tan2", 'tan3', "tan4"))+
stat_summary(fun=mean, geom="point", color="blue")+
coord_flip()

ggarrange(p2, p3, p4,
          ncol = 1,
          nrow = 1)
```


```{r}
ordered_Charges <- insurance[order(-insurance$charges), ]

head(ordered_Charges)

tail(ordered_Charges)
```


```{r}
boxplot.stats(insurance$charges)
```

### Age

```{r}
brx_age <- pretty(range(insurance$age),
              n = nclass.Sturges(insurance$age), min.n = 1)

Age1 <- ggplot(insurance) +
  geom_histogram(aes(x=age), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_age) +
  geom_vline(aes(xintercept=mean(age)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Age", y="Count") +
  theme_classic()

Age2 <- ggplot(insurance, aes(x = "", y=age)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Age") +
  theme_minimal()

Age3 <- ggplot(insurance, aes(age)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Age") +
  theme_classic()

Age4 <- ggplot(insurance) +
  geom_point(aes(x=age, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Age")

ggarrange(Age1, Age2, Age3, Age4,
          ncol = 2,
          nrow = 2)
```

#### age & sex, charges
```{r}
as1<-ggplot(insurance, aes(x=sex, y=age, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="Age Distribution by sex")+
theme(plot.title = element_text(size=14))

as2<-ggplot(insurance, aes(x=age, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(as1, as2,
          ncol = 2,
          nrow = 1)
```

#### age & smoker, charges
```{r}
ass1<-ggplot(insurance, aes(x=smoker, y=age, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title="Age Distribution by smoker")+
theme(plot.title = element_text(size=14))

ass2<-ggplot(insurance, aes(x=age, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(ass1, ass2,
          ncol = 2,
          nrow = 1)
```

#### age & region, charges
```{r}
ar1<-ggplot(insurance, aes(x=region, y=age, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="Age Distribution by region")+
theme(plot.title = element_text(size=14))

ar2<-ggplot(insurance, aes(x=age, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Age x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(ar1, ar2,
          ncol = 2,
          nrow = 1)
```

#### Conclusion age

```{r}
ordered_Age <- insurance[order(-insurance$age), ]

head(ordered_Age)

tail(ordered_Age)
```

```{r}
boxplot.stats(insurance$age)
```

### Sex

```{r}
mode = function(){
    return(sort(-table(insurance$sex))[1])
}
 
mode()

sex = insurance$sex

sex.freq = table(sex)

pie(sex.freq, col=c('hotpink', "royalblue"))

SexBar <- ggplot(insurance) +
  geom_bar(aes(x=sex), width = 0.5, fill=c('hotpink', "royalblue"), color="black") +
  labs(title="",x="Sex", y="Count") +
  theme_classic()

ggarrange(SexBar)

```

```{r} 
table(insurance$sex) 
```
- There are 662 females and 676 males.

### Bmi

```{r}
brx_bmi <- pretty(range(insurance$bmi),
              n = nclass.Sturges(insurance$bmi), min.n = 1)

Bmi1 <- ggplot(insurance) +
  geom_histogram(aes(x=bmi), fill = wes_palette("Zissou1")[1], color="black", breaks = brx_bmi) +
  geom_vline(aes(xintercept=mean(age)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Bmi", y="Count") +
  theme_classic()

Bmi2 <- ggplot(insurance, aes(x = "", y=bmi)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Bmi") +
  theme_minimal()

Bmi3 <- ggplot(insurance, aes(bmi)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Bmi") +
  theme_classic()

Bmi4 <- ggplot(insurance) +
  geom_point(aes(x=bmi, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Bmi")

ggarrange(Bmi1, Bmi2, Bmi3, Bmi4,
          ncol = 2,
          nrow = 2)
```

#### bmi & sex, charges
```{r}
bs1<-ggplot(insurance, aes(x=sex, y=bmi, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="BMI Distribution by sex")+
theme(plot.title = element_text(size=14))

bs2<-ggplot(insurance, aes(x=bmi, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(bs1, bs2,
          ncol = 2,
          nrow = 1)
```

#### bmi & smoker, charges
```{r}
bss1<-ggplot(insurance, aes(x=smoker, y=bmi, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title="BMI Distribution by smoker")+
theme(plot.title = element_text(size=14))

bss2<-ggplot(insurance, aes(x=bmi, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(bss1, bss2,
          ncol = 2,
          nrow = 1)
```

#### bmi & region, charges
```{r}
br1<-ggplot(insurance, aes(x=region, y=bmi, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="BMI Distribution by region")+
theme(plot.title = element_text(size=14))

br2<-ggplot(insurance, aes(x=bmi, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="BMI x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(br1, br2,
          ncol = 2,
          nrow = 1)
```

#### Conclusion bmi

```{r}
ordered_Bmi <- insurance[order(-insurance$bmi), ]

head(ordered_Bmi)

tail(ordered_Bmi)
```

```{r}
boxplot.stats(insurance$bmi)
```

### Children 

```{r}
Child1 <- ggplot(insurance) +
  geom_bar(aes(x=children), fill = wes_palette("Zissou1")[1], color="black") +
  geom_vline(aes(xintercept=mean(children)), color="white", linetype="dashed", linewidth=1) +
  labs(title="",x="Children", y="Count") +
  theme_classic()

Child2 <- ggplot(insurance, aes(x = "", y=children)) +
  geom_boxplot(fill=wes_palette("Zissou1")[3], color="black") + labs(title = "", x = "", y = "Children") +
  theme_minimal()

Child3 <- ggplot(insurance, aes(children)) +
  stat_ecdf(geom="step") +
  labs(title="", y = "", x="Children") +
  theme_classic()

Child4 <- ggplot(insurance) +
  geom_point(aes(x=children, y=charges), shape=21, fill=wes_palette("Zissou1")[4], color="black") +
  labs(title="", y = "Charges", x="Children")

ggarrange(Child1, Child2, Child3, Child4,
          ncol = 2,
          nrow = 2)
```

#### children & sex, charges
```{r}
cs1<-ggplot(insurance, aes(x=sex, y=children, color=sex)) +
geom_sina()+
scale_color_manual(values=c('hotpink', "royalblue"))+
labs(title="Children Distribution by sex")+
theme(plot.title = element_text(size=14))

cs2<-ggplot(insurance, aes(x=children, y=charges, color= sex))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('hotpink', "royalblue"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by sex")+
theme(plot.title = element_text(size=14))

ggarrange(cs1, cs2,
          ncol = 2,
          nrow = 1)
```

#### children & smoker, charges
```{r}
css1<-ggplot(insurance, aes(x=smoker, y=children, color=smoker)) +
geom_sina()+
scale_color_manual(values=c('grey', "gold"))+
labs(title=" Children Distribution by smoker")+
theme(plot.title = element_text(size=14))

css2<-ggplot(insurance, aes(x=children, y=charges, color= smoker))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('gold', "grey"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by smoker")+
theme(plot.title = element_text(size=14))

ggarrange(css1, css2,
          ncol = 2,
          nrow = 1)
```

#### children & region, charges
```{r}
cr1<-ggplot(insurance, aes(x=region, y=children, color=region)) +
geom_sina()+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
labs(title="Children Distribution by region")+
theme(plot.title = element_text(size=14))

cr2<-ggplot(insurance, aes(x=children, y=charges, color= region))+
geom_jitter(alpha=0.3, size=2.5)+
scale_color_manual(values=c('tan1', "tan2", 'tan3', "tan4"))+
geom_rug()+
geom_smooth(method=lm, formula=y~x)+
labs(title="Children x Charges by region")+
theme(plot.title = element_text(size=14))

ggarrange(cr1, cr2,
          ncol = 2,
          nrow = 1)
```

Function for mode computation
```{r}
mode <- function(att){
    return(sort(-table(att))[1])
}
```


### Smoker
```{r}

 
mode(insurance$smoker)

smoker = insurance$smoker

smoker.freq = table(smoker)

pie(smoker.freq, col=c('grey', "gold"))

SmokerBar <- ggplot(insurance) +
  geom_bar(aes(x=smoker), width = 0.5, fill = c('grey', "gold"), color="black") +
  labs(title="",x="Smoker", y="Count") +
  theme_classic()

ggarrange(SmokerBar)
```

```{r} 
table(insurance$smoker) 
```
- 274 individals smoke and 1064 individuals doesn't smoke.

### Region
```{r}

mode(insurance$region)

region = insurance$region

region.freq = table(region)

pie(region.freq, col = c('tan1', "tan2", 'tan3', "tan4"))

RegionBar <- ggplot(insurance) +
  geom_bar(aes(x=region), width = 0.5, fill=c('tan1', "tan2", 'tan3', "tan4"), color="black") +
  labs(title="",x="Region", y="Count") +
  theme_classic()

ggarrange(RegionBar)
```


# Tests

**Is it the mean equal to 30?**

```{r}
t.test(insurance$bmi, mu = 30, 
       alternative="two.sided") # (one-tailed test)
```

The null hypothesis is mean = 30. 
The p-value is less than a significance level of 5%.
So we can reject the null hipothesis of mean = 30, and this means that the mean bmi is significantly different from 30.

**Shapiro test to see if it's normally distributed.**

```{r}
shapiro.test(insurance$bmi)
```

It is not normally distributed, so we use Wilcoxon test

```{r}
wilcox.test(insurance$bmi, mu = 30,  
            alternative="two.sided") # assuming the distribution is simetricaly aroud median
```

With p-value is less then 5%, we can reject the null hypothesis of mean = 30. 
The mean is statistical different from 30.


**Is the male bmi variance equal to the female bmi variance?**

```{r}
var.test(insurance[which(insurance$sex=="male"), "bmi"], 
         insurance[which(insurance$sex=="female"), "bmi"])
```

The null hypothesis is same variance. 
The p-values greater then the significance level of 0.05 allows us to accept the null hipothesis of two normal samples with same variance. 

**t-test**

```{r}
t.test(insurance[which(insurance$sex=="male"), "bmi"],
       insurance[which(insurance$sex=="female"), "bmi"], 
       alternative="two.sided", 
       var.equal= TRUE)
```

p-value greater than 0.05 so we can accept the null hypothesis of equal average bmi (not significantly different) between men and women.


**Shapiro Test for variable male**

```{r}
shapiro.test(insurance[which(insurance$sex=="male"), "bmi"])
```

**Shapiro Test for variable male**

```{r}
shapiro.test(insurance[which(insurance$sex=="female"), "bmi"])
```

The p-value smaller then 0.05 for both cases so we reject the null hipothesis of normally distribution.

**Wilcoxon test**

```{r}
wilcox.test(insurance[which(insurance$sex=="male"), "bmi"], 
            insurance[which(insurance$sex=="female"), "bmi"])
```

p-value greater then 5 % allow us to accept the null hipothesis of median bmi equal (not significantly diferent) for man and women.

## Anova Test
Test of the hypothesis used to determine whether there is a significant statistical difference between the averages of three or more groups of continuous data with respect to a category that differentiates them.


**Smoker**

```{r}
anova<-aov(bmi ~ smoker,  data=insurance)
summary(anova)
```

The p-value is 0.891, so we can't reject the null hypothesis of equal means.

```{r}
shapiro.test(x=residuals(object = anova))
```

**Kruskal Wallis**

The Kruskal–Wallis test by ranks or one-way ANOVA on ranks is a non-parametric method for testing whether samples originate from the same distribution. It is used for comparing two or more independent samples of equal or different sample sizes. The parametric equivalent of the Kruskal–Wallis test is the one-way analysis of variance (ANOVA).

```{r}
kruskal.test(bmi ~ smoker,  data=insurance)
```
The p-value is greater then 0.05 so we can conclude that there aren't significant differences between the treatment groups.


**Region**

```{r}
anova2<-aov(bmi ~ region,  data=insurance)
summary(anova2)
```

Low p-value, so we can reject the null hypothesis of equal means.

```{r}
shapiro.test(x=residuals(object = anova2))
```

```{r}
kruskal.test(bmi ~ region,  data=insurance)
```

## Correlation

Correlation is a statistical measure that expresses the extent to which two variables are linearly related.

```{r}
cor(insurance$charges, insurance$bmi)
```

There is no correlation between bmi and charges.


```{r}
cor(insurance$charges, insurance$age)
```

There is a low correlation between age and charges.


```{r}
cor(insurance$charges, insurance$children)
```

There is no correlation between children and charges


```{r}
aggregate(cbind(age, bmi, charges) ~ region + smoker,
  data = insurance,
  mean
)
```


```{r}
shapiro.test(insurance$charges)

shapiro.test(insurance$age)
```

Low p-values so we reject the null hypothesis of normality.


```{r}
cor.test(insurance$charges, insurance$age, method="kendall")
```

The low p-value would let us believe on a significant correlation. 0.47 can be considered a weak correlation.


# Regression

A linear regression is a statistical model that analyzes the relationship between a response variable (often called y) and one or more variables and their interactions (often called x or explanatory variables). You make this kind of relationships in your head all the time, for example when you calculate the age of a child based on her height, you are assuming the older she is, the taller she will be. 

```{r}
set.seed(703) #set seed (value) where value specifies the initial value of the random number seed.

training <- createDataPartition(insurance$charges, times=1, p=0.75, list=FALSE) 

data_regr<-insurance[training,]
data_test<-insurance[-training,]

regr <- lm(charges ~ age+sex+bmi+children+smoker, data = data_regr)

summary(regr)
```

```{r}
regr_pred<-predict(regr, data_test)

RMSE(regr_pred, data_test$charges)

R2(regr_pred, data_test$charges)
```

P-value of F-statistics is very low, so at least one predictor is really related to the outcome.
Besides the rmse of 5,853 and the r squared of 78%. Let's pay atttention to the coefficients (column Estimate) and their significance levels:
The intercept is -11979.14, and almost all the predictors (except sex) are significant, according to the p-values.

The interpretation of categorical variables, for example, "smoker", can be done like this: " the average charge increases 23519.69 if the individual smokes - with all other variables constant.

The coefficient value, when significant, is the average change on outcome with a unit increase on a predictor - with the others constant.
While the correlation measures the force on relationship, the coefficient quantifies the relationship and allows predictions with an equation.

Here, for example, for each additional unit in age, the expected average cost is 257.12 higher, after controlling the others variables.

### Assumptions of Linear Regression 

This method assumes that there is a linear relationship between predictors and outcome. The parameters will be estimated in order to give the best-fitted line, minimizing the sum of squared residuals (Ordinary Least Squares method). Linear regression has the advantage of interpretability, but there are some important checks to make.

Let's check some assumptions of linear regression:
- Linearity of data, linear relationship between x and y: Residuals x Fitted plot
- Normality of residuals: Normal QQ plot
- Homogeneity of residuals variance (homoscedasticity), residuals with constant variance: scale location plot

```{r}
options(repr.plot.width=20, repr.plot.height=20)

par(mfrow=c(1,1))

plot(regr)
```

At Residuals x Fitted plot, the non horizontal line may indicate a non-linear relationship.

The Normal Q-Q plot is used to verify the normal distribution of the pattern residues. On the x-axis we find theoretical quantiles, on the y-axis we find standardized residues.We see that the residuals are not exactly on the straight line, indicating that they are not normally distributed.

Scale-Location plot allows to display on the x-axis the values of the model regression and on the y axis the square root of standardized residues. The non straight line indicates heteroscedasticity.

To investigate the presence of outliers in the residues we analyze the graph Residuals vs Leverage. Leverage scores are between 0 and 1. A high leverage score is therefore close to 1. In our case the residues are between leverage scores between 0.00 and 0.02. From the graph we observe how residues are contained in the range -2 to 4. 


### Durbin Watson Test

We use the Durbin Watson coefficient to check for autocorrelation between residues. This coefficient is between 0 and 4. Values close to 2 indicate that there is no autocorrelation.

```{r}
durbinWatsonTest(regr)
```

Analyzing the test results we observe that the value of the Durbin-Watson coefficient is close to 2, that indicates the autocorrelation non-presence. 
To confirm this, the p-value is higher than the threshold value of 0.05; which does not allow us to reject the hypothesis that the residues are unrelated.


## Conclusion

At this point, we can consider the analysis finished. Thanks to the development of this analysis. we explored which variables such as: age, sex, children, smoking, bmi index affect for price of insurance in the region where data was collected.

For each attribute we did basic statistical analysis which help us understand relationship and effect caused on insurance charges. We notice that if an individual smoke and have an high bmi index, charges increase as well. Other consideration is that, aging and smoking affects the increase of charges.

During this analysis we built a regression model. The goal of linear regression is to find an equation to show the mathematical relationship between predictors and outcome.  As a result, the accuracy of this method is quite low, this indicates that the attributes of the dataset do not correlate linearly, but have a non-linear dependence. therefore, it will be appropriate to use non-linear models for further research.